### 2024-07-17 Article/Article-english.tex
typo

\noindent{\it Proof.}
    Let $H = \ker(\phi_\beta)$. Without loss of generality, we assume that the~rows of the~matrix $\beta$ are linearly independent
    over $Z$ (it is clear that the~rows expressed as a~linear combination of the~other rows can be removed from the~matrix $\beta$
    without changing the~kernel).

>>>>

\noindent{\it Proof.}
    Let $H = \ker(\phi_\beta)$. Without loss of generality, we assume that the~rows of the~matrix $\beta$ are linearly independent
    over $\mathbb{Z}$ (it is clear that the~rows expressed as a~linear combination of the~other rows can be removed from the~matrix $\beta$
    without changing the~kernel).
